Domain Tree Analysis

### 2017-08-22 domain_level/TextS4_domain_tree_analysis.Rmd
added in boxplot for domain and transcript expression

gg <- ggplot(sigUp_norm_counts_df, aes(x=Phenotype, y=`Proportion of VAR expression`
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`) + theme_bw()
gg <- gg + scale_colour_manual(values = colors)
gg
```

>>>>

gg <- ggplot(sigUp_norm_counts_df, aes(x=Phenotype, y=`Proportion of VAR expression`
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA) + geom_jitter(width = 0.2, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`, scales = "free_y") + theme_bw()
gg <- gg + scale_colour_manual(values = colors)
gg
```
